A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-08-20 summary.tex
edited summary

For locally isothermal disks $c^2_s=c_s^2(r)$ we generalize the vertical
shear instability (VSI) to include dust. We find that dust-loading
generally has a stabilizing effect. In our disk models
dust-loading does not affect VSI growth rates significantly, but
meridional motions may be suppressed at heights where vertical 
buoyancy dominates over vertical shear. These results are readily
understood by comparing the vertical shear rate with the buoyancy of
an isothermal, dusty gas which we have correctly identified.

>>>>

For locally isothermal disks $c^2_s=c_s^2(r)$ we generalize the vertical
shear instability (VSI) to include dust. We find that dust-loading
generally has a stabilizing effect. In our disk models
dust-loading does not affect VSI growth rates significantly, but
meridional motions may be suppressed at heights where dust-induced
vertical buoyancy dominates over vertical shear, consistent with our
previous study \citep{lin15}.

%These results are readily
%understood by comparing the vertical shear rate with the buoyancy of
%an isothermal, dusty gas which we have correctly identified.
